Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-03 draft.tex
begin revising proposition 1 for decisive war

\item \emph{For both players $g$ and $s$, $\frac {Q_{in}}{1-\delta} \geq  -\zeta_i+\frac{L_{in}(p_2) +W_{in}(p_1)+Q_{in}(1-p_1-p_2)}{1-\delta} \ \forall n$: in each period, the expected outcome under war is worse than the status quo.}

@@

\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $n$ may be reached because in period $n-1$ fighting resulted in a stalemate, both players ceded, or the status quo had been maintained, the strategic landscape in period $n$ is the same. Thus all periods in which the players are able to move are in an equivalence class in which the only possible strategic difference is in the value of the state variables.

@@

{\bf Proof of Lemma 1} \\
Recall that the upper case notation represents payoffs gross of investments by the outside players. Without loss of generality, consider the incentives to deviate for player $s$ in period $n$ given that the other three players play their equilibrium actions. Given the stationary equilibrium actions, playing Status Quo will lead to $Q_{sn} \ \forall n$, so the continuation value is $\frac{Q_{sn}}{1-\delta}$. Player $s$'s continuation value from the one-shot deviation to Cede, which leads to an absorbing state with payoff $L_{sn}$ in each period, is $\frac{L_{sn}}{1-\delta}$. The one-shot deviation to fight results in the war lottery, with a cost of $-\zeta_s$, $W_s$ forever with probability $p_1$, $L_s$ forever with probability $p_2$, and the status quo payoff forever with probability $1-p_1-p_2$. Thus the continuation value is $\zeta_s +\frac{W_{sn}(p_1)+ L_{sn}(p_2) +Q_{sn}(1-p_1-p_2)}{1-\delta}$.

>>>>

\item \emph{For both players $g$ and $s$, $\frac {Q_{in}}{1-\delta} \geq  -\zeta_i+\frac{W_{in}(p_1) + L_{in}(1-p_1)}{1-\delta} \ \forall n$: in each period, the expected outcome under war is worse than the status quo.}

@@

\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $n$ may be reached either because in period $n-1$ both players ceded or the status quo had been maintained, the strategic landscape in period $n$ is the same. Thus all periods in which the players are able to move are in an equivalence class in which the only possible strategic difference is in the value of the state variables.

@@

{\bf Proof of Lemma 1} \\
Recall that the upper case notation represents payoffs gross of investments by the outside players. Without loss of generality, consider the incentives to deviate for player $s$ in period $n$ given that the other three players play their equilibrium actions. Given the stationary equilibrium actions, playing Status Quo will lead to $Q_{sn} \ \forall n$, so the continuation value is $\frac{Q_{sn}}{1-\delta}$. Player $s$'s continuation value from the one-shot deviation to Cede, which leads to an absorbing state with payoff $L_{sn}$ in each period, is $\frac{L_{sn}}{1-\delta}$. The one-shot deviation to fight results in the war lottery, with a cost of $-\zeta_s$, $W_s$ forever with probability $p_1$, and $L_s$ forever with probability $1-p_1$. Thus the continuation value is $\zeta_s +\frac{W_{sn}(p_1)+ L_{sn}(1-p_1)}{1-\delta}$.
